Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-09 sections/srfm.tex
one more sentence on STED resolution
A few additions

  \caption{%
    \textbf{Principle of fluorescence microscopy.}
    \textbf{a:}
      Jablonski diagram of fluorescence. A photon of energy
      $h\nu_\text{ex}$ gets absorbed and excites the molecule from its
      electronic ground state $S_0$ to a vibrational excited state of the
      electronic state $S_1$ (green arrow). After radiation-less relaxation
      (black arrow) into the vibrational ground state of $S_1$, the molecule
      returns to any vibrational state of $S_0$ (red arrow) by emitting a photon
      of energy $h\nu_\text{em}$, after which it relaxes to the lowest
      vibrational state of $S_0$.
    \textbf{b:}
      Typical absorbance (green) and
      emission (red) spectra of a fluorescent dye molecule. Green and red
      rectangles indicate the wavelength range used for excitation (exc) and
      detection.
  }
  \label{fig:jablonski-fluorescence}
\end{figure}

Typical absorbance/emission spectra of fluorophores used as dyes in FM are
shown in Fig.~\ref{fig:jablonski-fluorescence}b. In FM, a single wavelength or
a wavelength range (green rectangle Fig.~\ref{fig:jablonski-fluorescence}b) in
suitable to excite the fluorophore used is chosen, by using a suitable laser
or LED or by selecting the wavelength range via a band-pass filter from a
white light source and send through the objective lens of the microscope to
the sample. In most FMs (the so called epifluorescence microscopes), the
emission is collected via the same objective lens. Since the emission is
red-shifted with respect to the excitation wavelength, the emitted photons
(wavelength range depicted by red rectangle in
Fig.~\ref{fig:jablonski-fluorescence}b) can be separated from the ones used to
excite the fluorophores by a dichroic mirror.

@@

The two most common implementations of FM used in the life sciences are the
wide-field and the confocal microscope. Both use a dichroic mirror to separate
excitation and emission, but their implementations differ in the way how the
sample is excited and how the emission is recorded. The beam paths and the
major components of a wide-field and a confocal FM are depicted in
Fig.~\ref{fig:FM-setups}. In a wide-field FM (Fig.~\ref{fig:FM-setups}a), the
entire sample is excited at 
the same time, and all fluorophores in the sample emit at the same time
(yellow circles in the right inset in Fig.~\ref{fig:FM-setups}a). The emission
of the fluorophores (solid red shape in Fig.~\ref{fig:FM-setups}a, only five
beam paths are shown for clarity) is collected by the objective lens, passes
the dichroic mirror and is further cleared by a band-pass filter. The emission
then is focused by the tube lens onto the camera, which records an image of
the emission of all fluorophores at the same time.

Each fluorophore in the sample generates a diffraction limited spot on the
camera, and spots which are not separated in space by at least the diffraction
cannot be distinguished as single spots. Thus, the wavelength which determines
the resolution in a wide-field microscope is the wavelength $\lambda_\text{em}$
of the emission.

The major disadvantage of a wide-field microscope is that the sample is not
only illuminated evenly in the focal plane of the objective lens, but also
fluorophores outside the focal plane in $z$-direction are excited and their
emission is collected (not shown for clarity). Since they are not located in
the focal plane of the objective lens, their emission does not result in a
sharp spot on the camera, but instead appears as a blurred background.

This led to the invention of the confocal microscope
\cite{Heimstaedt1911,Minsky1988}. The beam path of a confocal microscope is
shown in Fig.~\ref{fig:FM-setups}b. Here, the excitation light (green solid
shape) is focused into the sample by the objective lens and only the
fluorophores within the diffraction limited spot are excited. Thus, the
wavelength which determines the resolution of a confocal microscope is the
excitation wavelength $\lambda_\text{ex}$.  In contrast to the wide-field
microscope, the emission of the fluorophores is focused onto a pinhole which
is located in front of a single detector (left inset in
Fig.~\ref{fig:FM-setups}b). Since this setup does not allow imaging the entire
sample at once, the sample has to be scanned with respect to the excitation
light beam and the image is collected pixel by
pixel. Fig.~\ref{fig:FM-setups}c illustrates the major effect of the pinhole:
Emission from out-of-focus planes (dotted and dashed lines) is blocked by the
pinhole since it is located in the same focal plane as the sample (thus the
name \emph{confocal}).

@@

As an example for RESOLFT, the principle of STED microscopy is sketched in
Fig.~\ref{fig:STED-principle}. The excitation spot
(Fig.~\ref{fig:STED-principle}a, top) is superimposed with a second, ring- or
doughnut-shaped spot (Fig.~\ref{fig:STED-principle}a, bottom). The
fluorophores are excited by the excitation light, but only those located in
the center of the minimum of the depletion beam are allowed to emit
spontaneously (yellow dot). The fluorophores at the periphery are de-excited
by the depletion beam and undergo stimulated emission (black dots). The
Jablonski diagram of stimulated emission is shown in
Fig.~\ref{fig:STED-principle}c (left). An incoming photon of the depletion
beam interacts with the excited fluorophore and causes it to de-excite to the
ground state and to emit a photon of the same energy as the incoming
photon. Due to the non-linear relation between intensity and the probability
to induce stimulated emission and the shape of the depletion beam
(Fig.~\ref{fig:STED-principle}c, center), the size of the origin of
spontaneous emission in the center of the depletion beam is decreased. The
wavelength of the depletion beam and thus the wavelength of stimulated
emission is selected such that it lies outside the detection window of the
microscope (Fig.~\ref{fig:STED-principle}c, right), which de-facto switches
fluorophores that undergo stimulated emission to an ``off''-state.

@@

>>>>

  \caption{%
    \textbf{Principle of fluorescence microscopy.}  \textbf{a:} Jablonski
    diagram of fluorescence. A photon of energy $h\nu_\text{ex}$ gets absorbed
    and excites the molecule from its electronic ground state $S_0$ to a
    vibrational excited state of the electronic state $S_1$ (green
    arrow). After radiation-less relaxation (black arrow) into the vibrational
    ground state of $S_1$, the molecule returns to one of the vibrational
    states of $S_0$ (red arrow) by emitting a photon of energy
    $h\nu_\text{em}$, after which it relaxes to the lowest vibrational state
    of $S_0$.  \textbf{b:} Typical absorbance (green) and emission (red)
    spectra of a fluorescent dye molecule. Green and red rectangles indicate
    the wavelength range used for excitation (exc) and detection in FM.  }
  \label{fig:jablonski-fluorescence}
\end{figure}

Typical absorbance/emission spectra of fluorophores used as dyes in FM are
shown in Fig.~\ref{fig:jablonski-fluorescence}b. In FM, a single wavelength or
a wavelength range (green rectangle in Fig.~\ref{fig:jablonski-fluorescence}b) 
suitable to excite the fluorophore used is chosen -- by using a suitable laser
or LED or by selecting the wavelength range via a band-pass filter from a
white light source -- and send through the objective lens of the microscope to
the sample. In most FMs (the so called epifluorescence microscopes), the
emission is collected via the same objective lens. Since the emission is
red-shifted with respect to the excitation wavelength, the emitted photons
(wavelength range depicted by red rectangle in
Fig.~\ref{fig:jablonski-fluorescence}b) can be separated from the ones used to
excite the fluorophores by a dichroic mirror.

@@

The two most common implementations of FM used in the life sciences are the
wide-field and the confocal microscope. Both use a dichroic mirror to separate
excitation and emission, but their implementations differ in the way how the
sample is excited and how the emission is recorded. The beam paths and the
major components of a wide-field and a confocal FM are depicted in
Fig.~\ref{fig:FM-setups}. In a wide-field FM (Fig.~\ref{fig:FM-setups}a), the
entire sample is illuminated at the same time, and all fluorophores in the sample
emit at the same time (yellow circles in the right inset in
Fig.~\ref{fig:FM-setups}a). The emission of the fluorophores (solid red shape
in Fig.~\ref{fig:FM-setups}a, only five beam paths are shown for clarity) is
collected by the objective lens, passes the dichroic mirror and is further
cleared by a band-pass filter. The emission then is focused by the tube lens
onto the camera, which records an image of the emission of all fluorophores at
the same time.

Each fluorophore in the sample generates a diffraction limited spot on the
camera, and spots which are not separated in space by at least the diffraction limit
cannot be distinguished as single spots. Thus, the wavelength which determines
the resolution in a wide-field microscope is the wavelength $\lambda_\text{em}$
of the emission.

The major disadvantage of a wide-field microscope is that the sample is not
only illuminated in the focal plane of the objective lens, but also
fluorophores above and below the focal plane are excited and their
emission is collected (not shown for clarity). Since they are not located in
the focal plane of the objective lens, their emission does not result in a
sharp spot on the camera, but instead appears as a blurred background.

This led to the invention of the confocal microscope
\cite{Heimstaedt1911,Minsky1988}. The beam path of a confocal microscope is
shown in Fig.~\ref{fig:FM-setups}b. Here, the excitation light (green solid
shape) is focused onto the sample by the objective lens and only the
fluorophores within the resulting diffraction limited spot are excited. Thus, the
wavelength which determines the resolution of a confocal microscope is the
excitation wavelength $\lambda_\text{ex}$.  In contrast to the wide-field
microscope, the emission of the fluorophores is focused onto a pinhole which
is located in front of a single detector (left inset in
Fig.~\ref{fig:FM-setups}b). Since this setup does not allow imaging the entire
sample at once, the sample has to be scanned with respect to the excitation
light beam and the image is collected pixel by
pixel. Fig.~\ref{fig:FM-setups}c illustrates the major effect of the pinhole:
Emission from out-of-focus planes (dotted and dashed lines) is blocked by the
pinhole since it is located in the same focal plane as the sample (thus the
name \emph{confocal}).

For a potential combination with SICM, the most important aspect of the two
techniques is the way the fluorescence is recorded. Wide-field FM uses a 
camera to record the entire sample at once, whereas confocal FM is a scanning
technique which records the single pixels subsequently, either by moving the
sample through the beam or vice versa.

@@

As an example for RESOLFT, the principle of STED microscopy is sketched in
Fig.~\ref{fig:STED-principle}. The excitation spot
(Fig.~\ref{fig:STED-principle}a, top) is superimposed with a second, ring- or
doughnut-shaped spot (Fig.~\ref{fig:STED-principle}a, bottom). The
fluorophores are excited by the excitation light, but only those located in
the center of the minimum of the depletion beam are allowed to emit
spontaneously (yellow dot). The fluorophores at the periphery are de-excited
by the depletion beam and undergo stimulated emission (black dots). The
Jablonski diagram of stimulated emission is shown in
Fig.~\ref{fig:STED-principle}c (left). An incoming photon of the depletion
beam interacts with the excited fluorophore and causes it to de-excite to the
ground state and to emit a second photon of the same energy as the incoming
photon. Due to the non-linear relation between intensity and the probability
to induce stimulated emission and the shape of the depletion beam
(Fig.~\ref{fig:STED-principle}c, center), the size of the origin of
spontaneous emission in the center of the depletion beam is decreased. The
wavelength of the depletion beam and thus the wavelength of stimulated
emission is selected such that it is outside the detection window of the
microscope (Fig.~\ref{fig:STED-principle}c, right), which de-facto switches
fluorophores that undergo stimulated emission to an invisible ``off''-state.

@@

The best resolution (approximately 2\,nm) obtained by STED microscopy has
been recorded on samples containing fluorescent color centers in diamond
crystal \cite{Wildanger2012}. Note that, by applying a depletion beam of a
different shape, STED microscopy allows to improve the resolution along the
optical axis \cite{Wildanger2009}. A large number of reviews articles exist
which summarize the use of STED (or in general, RESOLFT) microscopy in different
fields in the life sciences, much too much to be listed here. We would like to
refer the reader to exhaustive reviews, which, besides
reviewing various applications, detail technical aspects of STED microscopy
\cite{Turkowyd2016,Blom2017} as well as to a review which contains some
anecdotal sections on how STED was developed \cite{Sahl2019}.
